---
title: "VR-Training Project"
subtitle: "by Fabio Genz and Dieter Kranzlmüller"
author: "Arsine Chinaryan, Anh Hoang Minh Dang, Iris Dizdari, Margarita Khachatryan"
institute: "Supervisor: Daniel Schlichting"
date: "2024-2-13"
format: 
  revealjs:
    css: customstyle.css
    embed-resources: true
    slide-number: true
    logo: "LMULogo.jpg"
editor: visual
---

```{r setup, include=FALSE}
source("environmentSetUp.R")
source("Analysis/correlationPlot.R")
source("Analysis/correlationRoundPlot.R")
```

## Outline

::: incremental
1.  Overview & Terminology

2.  Data analysis

    -   Relationship between Stress indicators and Physiological Measurements\
    -   Relationship over the rounds\
    -   Subgroups' behavior\
    -   Cohorts comparison

3.  Summary and Discussion
:::

## Overview

**VR-Training**: Adapting Virtual Reality Training Applications by Dynamically Adjusting Visual Aspects\
**Author**: Fabio Genz and Dieter Kranzlmüller

::: incremental
-   **Survey**: Cross-sectional study with longitudinal elements

-   2 Cohorts (Linne and Dame)

    -- 21 participants in Linne, 81 in Dame (with overlaps)

    -- 9 rounds of training for both cohorts

    -- Grouped into Adative and Non-Adaptive training versions

    -- 2 rounds of test per cohort (Linne: VR, Dame: Real-world)

-   **Timeframe**:
:::

## Terminology

### Stress indicators:

-   **Answer Q1**: Perceived cognitive load (1 to 6 with 1 very low and 6 very high)
-   **Answer Q2**: Perceived physical load (1 to 6 with 1 very low and 6 very high)

## Terminology

### Physiological Measurement Data (PMD)

::: columns
::: {.column width="50%"}
-   **Heart rate (HR)**: Heart rate beats per minute (bpm)\
-   **IBI**: Interbeat interval (ms)\
-   **SDNN**: Standard deviation of the NN intervals\
-   **RMSSD**: Root mean square of successive differences\
-   **SCL**: Skin conductance level (µS (micro Siemens))\
-   **SCR frequency**: Frequency of the skin conductance response
:::

::: {.column width="50%"}
-   **SCR amplitude**: Amplitude/strength of the skin conductance response (µS/µmho (micro Siemens/micro Ohm))
-   **SCR rising time**: Rising time of the skin conductance response\
-   **Blink rate last minute**: Blink frequency per minute\
-   **Saccade amplitude**: Degree of eye movement\
-   **Saccade velocity**: Speed of sudden eye movements\
:::
:::

## Outline

[1. Overview & Terminology]{style="color:lightgray;"}

2.  Data Analysis

    Relationship between Stress indicators and Physiological Measurements\
    [Relationship over the rounds]{style="color:lightgray;"}\
    [Subgroups' behavior]{style="color:lightgray;"}\
    [Cohorts comparison]{style="color:lightgray;"}

[3. Summary and Discussion]{style="color:lightgray;"}

## Relationship between Stress indicator and Physical Measurements {style="font-size: 26px;"}

```{r}
dameQ1
```

## Relationship between Stress indicator and Physical Measurements {style="font-size: 26px;"}

```{r}
dameQ2
```

## Relationship between Stress indicator and Physical Measurements {style="font-size: 26px;"}

```{r}
linneQ1
```

## Relationship between Stress indicator and Physical Measurements {style="font-size: 26px;"}

```{r}
linneQ2
```

## Outline

[1. Overview & Terminology]{style="color:lightgray;"}

2.  Data Analysis

    [Relationship between Stress indicators and Physiological Measurements]{style="color:lightgray;"}\
    Relationship over the rounds\
    [Subgroups' behavior]{style="color:lightgray;"}\
    [Cohorts comparison]{style="color:lightgray;"}

[3. Summary and Discussion]{style="color:lightgray;"}

## Relationship over the rounds

```{r}
roundDameQ1
```

## Relationship over the rounds

```{r}
roundDameQ2
```

## Relationship over the rounds

```{r}
roundLinneQ1
```

## Relationship over the rounds

```{r}
roundLinneQ2
```
