---
title: "VR-Training Project"
author: "Arsine Chinaryan, Anh Hoang Minh Dang, Iris Dizdari, Margarita Khachatryan"
institute: "Dr. Fabian Scheipl, Dr. Sabine Hoffmann, Daniel Schlichting"
date: "2024-2-13"
format: 
  revealjs:
    css: customstyle.css
    embed-resources: true
    slide-number: c
editor: visual
---

```{r setup, include=FALSE}
source("environmentSetUp.R")
source("Analysis/correlationPlot.R")
source("Analysis/correlationRoundPlot.R")
source("Analysis/subgroupPlot.R")
source("Analysis/cohortDifferences.R")
```

## Outline

::: incremental 
1. Overview & Terminology

2.  Data analysis

    -   Relationship between Stress indicators and Physiological Measurements\
    -   Relationship over the rounds\
    -   Subgroups and Outliers\
    -   Cohorts comparison: Similarities and Differences

3.  Summary and Discussion
:::

## Overview of the VR Project

**VR-Training**: Adapting Virtual Reality Training Applications by Dynamically Adjusting Visual Aspects

**Motivation:**\
- Static training doesn't fit everyone: Too easy → boredom, Too hard → anxiety\
- Adaptive VR training balances difficulty to improve outcomes.

**Scenario:**\
- Users move and place parcels in a VR warehouse using controllers.\
- Visual cues: dynamic lighting and color guidance.

**Adaptive Features:**\
- Tracks user behavior (head movement) and performance (time, errors).\
- Adjusts lighting, object colors, etc., after each training round.

## Terminology

### Stress indicators:

-   Perceived cognitive load (1 to 6 with 1 very low and 6 very high)
-   Perceived physical load (1 to 6 with 1 very low and 6 very high)

### Physiological Measurement Data (PMD)

-   **Heart measurements:** Heart rate (HR), SDNN, RMSSD
-   **Skin conductance response (SCR) measurements:** Skin conductance level (SCL), SCR frequency, SCR amplitude, SCR rising time
-   **Eye tracking measurements:** Blink rate per minute, Saccade amplitude, Saccade velocity

## Outline

[1. Overview & Terminology]{style="color:lightgray;"}

2.  Data Analysis

    Relationship between Stress indicators and Physiological Measurements\
    [Relationship over the rounds]{style="color:lightgray;"}\
    [Subgroups and Outliers]{style="color:lightgray;"}\
    [Cohorts comparison: Similarities and Differences]{style="color:lightgray;"}

[3. Summary and Discussion]{style="color:lightgray;"}

## Relationship between Stress indicator and Physical Measurements {style="font-size: 26px;"}

```{r}
correlationDame
```

## Relationship between Stress indicator and Physical Measurements {style="font-size: 26px;"}

```{r}
correlationLinne
```

## Outline

[1. Overview & Terminology]{style="color:lightgray;"}

2.  Data Analysis

    [Relationship between Stress indicators and Physiological Measurements]{style="color:lightgray;"}\
    Relationship over the rounds\
    [Subgroups and Outliers]{style="color:lightgray;"}\
    [Cohorts comparison: Similarities and Differences]{style="color:lightgray;"}

[3. Summary and Discussion]{style="color:lightgray;"}

## Relationship over the rounds

```{r}
roundDameQ1
```

## Relationship over the rounds

```{r}
roundDameQ2
```

## Relationship over the rounds

```{r}
roundLinneQ1
```

## Relationship over the rounds

```{r}
roundLinneQ2
```

## Outline

[1. Overview & Terminology]{style="color:lightgray;"}

2.  Data Analysis

    [Relationship between Stress indicators and Physiological Measurements]{style="color:lightgray;"}\
    [Relationship over the rounds]{style="color:lightgray;"}\
    Subgroups and Outliers\
    [Cohorts comparison]{style="color:lightgray;"}

[3. Summary and Discussion]{style="color:lightgray;"}

## Stress resilient groups

```{r}
hrvQ1ByAgeDame
```

[-- All participants with high HRV values belong to the Adapted training version.]{style="font-size: 18px;"}

## Stress resilient groups

```{r}
hrQ1TrainingMalesLinne
```

## Stress resilient groups

```{r}
hrQ1TrainingMalesDame
```

## Outline

[1. Overview & Terminology]{style="color:lightgray;"}

2.  Data Analysis

    [Relationship between Stress indicators and Physiological Measurements]{style="color:lightgray;"}\
    [Relationship over the rounds]{style="color:lightgray;"}\
    [Subgroups' behavior]{style="color:lightgray;"}\
    Cohorts comparison

[3. Summary and Discussion]{style="color:lightgray;"}

## Cohort comparison

```{r}
ageVariability + genderDistribution
```

## Cohort comparison

```{r}
BMI
```

## Cohort comparison

```{r}
AnswerQ1 + AnswerQ2
```

## Cohort comparison

```{r}
RMSSD + SDNN
```
