---
title: "VR-Training Project"
subtitle: "by Fabio Genz and Dieter Kranzlmüller"
author: "Arsine Chinaryan, Anh Hoang Minh Dang, Iris Dizdari, Margarita Khachatryan"
institute: "Supervisor: Daniel Schlichting"
date: "2024-2-13"
format: 
  revealjs:
    css: customstyle.css
    embed-resources: true
    slide-number: true
    logo: "LMULogo.jpg"
editor: visual
---
```{r setup, include=FALSE}
source("../../environmentSetUp.R")
source("../../Script/plot/correlationPlot.R")
```

## Outline

::: incremental
1.  Overview & Terminology

2.  Data analysis


    -   Relationship between perceived Stress and Physical Measurements\
    -   Relationship over the rounds\
    -   Subgroup behavior\
    -   Cohort comparison


3.  Summary and Discussion
:::

## Overview

**VR-Training**: Adapting Virtual Reality Training Applications by Dynamically Adjusting Visual Aspects\

::: incremental
-   **Survey**: Cross-sectional Study with Longitudinal Elements

-   2 Cohorts (Linne and Dame)

    -- 21 Participants in Linne, 81 in Dame (with overlaps)

    -- 9 Rounds of Training for Dame and 11 for Linne

    -- Grouped into Adative and Non-Adaptive Training versions

    -- 2 Rounds of Test per Cohort (Linne: VR, Dame: Real-world)

-   **Timeframe**:
:::

## Terminology

### Stress indicators:

-   **Answer Q1**: Perceived cognitive load ({1,2,3,4,5,6} with 1 very low and 6 very high)
-   **Answer Q2**: Perceived physical load ({1,2,3,4,5,6} with 1 very low and 6 very high)

## Terminology

SORT AGAIN AND TAKE OUT WHAT IS UNNECESSARY

### Physiological measurement data (PMD)

-   **Heart rate (HR)**: Heart rate beats per minute (bpm)
-   **IBI**: Interbeat interval (ms)
-   **SDNN**: Standard deviation of the NN intervals
-   **RMSSD**: Root mean square of successive differences
-   **SCL**: Skin conductance level (µS (mikro Siemens))
-   **SCR amplitude**: Amplitude/strength of the skin conductance response (µS/µmho (mikro Siemens/mikro Ohm))
-   **SCR frequency**: Frequency of the skin conductance response
-   **SCR_rising_time**: Rising time of the skin conductance response
-   **Blink rate last minute**: Blink frequency per time unit
-   **Saccade amplitude**: Degree of eye movement
-   **Saccade velocity**: Speed of sudden eye movements

## Outline

[1. Overview & Terminology]{style="color:lightgray;"}

2.  Data Analysis

    Relationship between Stress indicator and Physical Measurements\
    [Relationship over the Rounds]{style="color:lightgray;"}\
    [Subgroup Behavior]{style="color:lightgray;"}\
    [Cohort Comparison]{style="color:lightgray;"}

[3. Summary and Discussion]{style="color:lightgray;"}


## Relationship between Stress indicator and Physical Measurements

```{r}
dameQ1
```















